Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-21 paper/paper.tex
made changes necc for Makefile to work with new file structure Tested everything on quipu.

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500-exact}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-plot--p-300-50-0-0-1500-full_array}
  \caption{Countour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}

@@

\begin{figure}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500-exact}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500-exact}
  \caption{Box plots of Mannik shapes for sizes at the lower stability
    threshhold.  The vertical axis shows stacked and changing over
    time the total number of proteins that are of four different
    compound stages and in the different sections of the cell.  Both
    shapes have longer axis of roughly 2.2$\mu m$.}
  \label{box-mannik}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/plot-time-averaged-arrow-500-520-NflD-stad-25-400-150-0-1500-full_array}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-600-200-0-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-400-150-0-1500-full_array}
  \caption{Time map plots of our stad shape}
  \label{time-maps-stad}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1850-1850-9500-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2500-2500-9500-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1860-2860-9400-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2300-3200-9400-1500-full_array}
  \caption{Time map plots of our randst shape}
  \label{time-maps-randst}
\end{figure}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
  \caption{Countour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}

@@

\begin{figure}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-8_00-8_00-95_00-15_00-exact/plots/box-plot_D}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-10_00-17_00-94_00-15_00-exact/plots/box-plot_D}
  \caption{Box plots of Mannik shapes for sizes at the lower stability
    threshhold.  The vertical axis shows stacked and changing over
    time the total number of proteins that are of four different
    compound stages and in the different sections of the cell.  Both
    shapes have longer axis of roughly 2.2$\mu m$.}
  \label{box-mannik}
\end{figure}

@@

\begin{figure}

  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/NflD-time-map}
  \caption{Time map plots of our stad shape}
  \label{time-maps-stad}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/NflD-time-map}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/NflD-time-map}
  \caption{Time map plots of our randst shape}
  \label{time-maps-randst}
\end{figure}
